Graph Generators: State of the Art and Open Challenges

### 2019-08-06 comparison.tex
Adding RTG
Irena's pass (plagiarism) pp 1-10

In order to provide the reader with a general preview of the generators and  to enable finding the target solutions easily, we start the survey with a  classification and comparative study of the existing tools. In general, there are various ways to classify them. We first provide an overview of the approaches used in related work after which we then introduce our approach. As mentioned in the Introduction, since this survey is unique especially in terms of scope, our classification and comparative strategy differs as well.

The graph data generators can be classified according to various criteria. For example,~\cite{DBLP:conf/sdm/ChakrabartiZF04} introduces two categories -- degree-based and procedural generators. In general, \emph{degree-based generators} (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) are commonly attempting to find a graph that matches it, but without providing any information about the graph or attempting to match other graph features (e.g., eigenvalues, small diameter, etc). On the other hand, \emph{procedural generators} (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) are commonly targeting simple techniques to produce graphs that are matching the characteristics of the real-world graphs (e.g., the power law degree distribution).

Paper~\cite{Chakrabarti:2006:GML:1132952.1132954} introduces five categories of graph models that can be synthesized: (1) \emph{random graph models} (e.g., Erd\"{o}s-R\'{e}nyi~\cite{Erdos:1960}) generated by a random process, (2) \emph{preferential attachment models} (e.g., Barabasi-Albert model) which try to model the power law from the preferential attachment viewpoint, (3) \emph{optimization-based models} (e.g., HOT model~\cite{PhysRevLett.84.2529}) resulting from the idea that power laws can result from resource optimizations and tolerance to risks, (4) \emph{tensor-based models} (e.g., R-MAT) targeting a trade-off between low number of model parameters and efficiency, and (5) \emph{internet-specific models} corresponding to hybrids using ideas from the other categories in order to suit the specific features of the graphs.

@@

\multirow{6}{*}{\rot{\textbf{General}}}

@@

@@

\begin{table}
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               %& \textbf{\rot{Analytics}}
               & \textbf{\rot{Community detection\ }}
               %& \textbf{\rot{Streaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{6}{*}{\rot{\textbf{General}}}
  & Preferential attachment & {\bf x} & & &  & \\
\cline{2-7}
   & R-MAT    & {\bf x} & & &  &  \\
\cline{2-7}
   & HPC Scal. Graph Anal.  & {\bf x} & & &  &  \\
\cline{2-7}
  & GraphGen  & {\bf x} & & x &  & \\
\cline{2-7}
%  & Graph 500 & {\bf x} & & &  & \\
%\cline{2-7}
  & BTER      & {\bf x} & & &  & \\
\cline{2-7}
  & Darwini   & {\bf x} & & &  & \\
\hline
\hline %  ======================  Semantic web
\multirow{16}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & {\bf x} & &  &  \\
\cline{2-7}
 & LBBM  & & {\bf x} & &  &  \\
\cline{2-7}
 & UOBM  & & {\bf x} & &  &  \\
\cline{2-7}
 & IIMB & & {\bf x} & &  & \\
\cline{2-7}
 & BSBM & & {\bf x} & &  &  \\
\cline{2-7}
 & SP$^2$Bench & & {\bf x} & &  &  \\
\cline{2-7}
 & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & &  &  \\
\cline{2-7}
 & DBPSB & & {\bf x} & &  &  \\
\cline{2-7}
 & LODIB & & {\bf x} & &  &  \\
\cline{2-7}
% & SIB & & {\bf x} & &  &  \\
%\cline{2-7}
 & Geographica & & {\bf x} & &  &  \\
\cline{2-7}
 & WatDiv & & {\bf x} & &  &  \\
\cline{2-7}
 & RBench & & {\bf x} & &  &  \\
\cline{2-7}
  & S2Gen & & {\bf x} & &  &  \\
\cline{2-7}
  & RSPLab & & {\bf x} & &  &  \\
\cline{2-7}
 & LDBC SPB & & {\bf x} & &  &  \\
\cline{2-7}
 & LinkGen & & {\bf x} & &  &  \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & {\bf x} & x  &  \\
\cline{2-7}
  & gMark & & x & {\bf x} & x  &  \\
\cline{2-7}
  & graphGen & & & {\bf x} &  &  \\
\hline
\hline %  ======================   social networks
\multirow{8}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x}  & \\
\cline{2-7}
 & \cite{Yao2011}  & & & & {\bf x}  & \\
\cline{2-7}
 & LinkBench  & & & x & {\bf x}  & \\
\cline{2-7}
 & S3G2  & & x & x & {\bf x}  & \\
\cline{2-7}
 & SIB & & x & & {\bf x}  &  \\
\cline{2-7}
 & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x}  & \\
\cline{2-7}
 & LDBC SNB   & & x & x & {\bf x}  & \\
\cline{2-7}
  & \cite{Nettleton2016}  & & & & {\bf x}  &  \\
%\hline
%\hline   % ======================   graph analytics
%\multirow{1}{*}{\rot{\textbf{A}}}
%  & HPC Scal. Graph Anal.  & & & & &  \\
%\cline{2-7}
%  & Graphalytics & & & & &  \\
\hline
\hline   %  ======================  community detection
\multirow{4}{*}{\rot{\textbf{Co}}}
  & \cite{danon2005comparing} & x & & & &  {\bf x} \\
\cline{2-7}
  & LFR & x & & & &  {\bf x}  \\
\cline{2-7}
  & LFR-Overlapping & x & & & &  {\bf x} \\
\cline{2-7}
  & Stochastic Block Models & x & & & &  {\bf x} \\
%\cline{2-7}
%  & & & & &  \\
\hline
%\hline   %  ======================  streaming
%\multirow{2}{*}{\rot{\textbf{St}}}
%  & S2Gen & & & & & & & {\bf x}\\
%\cline{2-7}
%  & RSPLab & & & & & & & {\bf x} \\
%%\cline{2-7}
%%  & & & & & & \\
%\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

>>>>

In order to provide a general preview of the generators and  to enable finding the target solutions easily, we start the survey with a  classification and comparative study of the existing tools. In general, there are various ways to classify them. We first offer an overview of the approaches used in state-of-the-art work after which we then introduce our approach. As mentioned in the Introduction, since this survey is unique especially in terms of scope, our classification and comparative strategy differs as well.

The graph data generators can be classified using various distinct criteria. For example,~\cite{DBLP:conf/sdm/ChakrabartiZF04} introduces two categories -- degree-based and procedural generators. In general, \emph{degree-based generators} (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) are commonly attempting to find a graph that matches it, but without providing any information about the graph or attempting to match other graph features (e.g., eigenvalues, small diameter, etc). On the other hand, \emph{procedural generators} (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) are commonly targeting simple techniques to produce graphs that are matching the characteristics of the real-world graphs (such as, e.g., the power law degree distribution).

Paper~\cite{Chakrabarti:2006:GML:1132952.1132954} introduces five categories of graph models that can be synthesized: (1) \emph{random graph models} (e.g., Erd\"{o}s-R\'{e}nyi~\cite{Erdos:1960}) generated by a random process, (2) \emph{preferential attachment models} (e.g., Barabasi-Albert model) which try to model the power law from the preferential attachment viewpoint, (3) \emph{optimization-based models} (e.g., HOT model~\cite{PhysRevLett.84.2529}) resulting from the idea that power laws can result from tolerance to risks and resource optimizations, (4) \emph{tensor-based models} (e.g., R-MAT) targeting a trade-off between low number of model parameters and efficiency, and (5) \emph{internet-specific models} corresponding to hybrids using ideas from the other categories in order to suit the specific features of the graphs.

@@

\multirow{7}{*}{\rot{\textbf{General}}}

@@

  & RTG & -- & -- &   N & N & N & power-law &  edge-list & N  \\

@@

\begin{table}
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               %& \textbf{\rot{Analytics}}
               & \textbf{\rot{Community detection\ }}
               %& \textbf{\rot{Streaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{6}{*}{\rot{\textbf{General}}}
  & Preferential attachment & {\bf x} & & &  &  \\
\cline{2-7}
   & R-MAT    & {\bf x} & & &  &  \\
\cline{2-7}
   & HPC Scal. Graph Anal.  & {\bf x} & & &  &  \\
\cline{2-7}
  & GraphGen  & {\bf x} & & x &  & \\
\cline{2-7}
%  & Graph 500 & {\bf x} & & &  & \\
%\cline{2-7}
  & BTER      & {\bf x} & & &  & \\
\cline{2-7}
  & Darwini   & {\bf x} & & &  & \\
\cline{2-7}
  & RTG   & {\bf x} & & &  & x \\
\hline
\hline %  ======================  Semantic web
\multirow{16}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & {\bf x} & &  &  \\
\cline{2-7}
 & LBBM  & & {\bf x} & &  &  \\
\cline{2-7}
 & UOBM  & & {\bf x} & &  &  \\
\cline{2-7}
 & IIMB & & {\bf x} & &  & \\
\cline{2-7}
 & BSBM & & {\bf x} & &  &  \\
\cline{2-7}
 & SP$^2$Bench & & {\bf x} & &  &  \\
\cline{2-7}
 & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & &  &  \\
\cline{2-7}
 & DBPSB & & {\bf x} & &  &  \\
\cline{2-7}
 & LODIB & & {\bf x} & &  &  \\
\cline{2-7}
% & SIB & & {\bf x} & &  &  \\
%\cline{2-7}
 & Geographica & & {\bf x} & &  &  \\
\cline{2-7}
 & WatDiv & & {\bf x} & &  &  \\
\cline{2-7}
 & RBench & & {\bf x} & &  &  \\
\cline{2-7}
  & S2Gen & & {\bf x} & &  &  \\
\cline{2-7}
  & RSPLab & & {\bf x} & &  &  \\
\cline{2-7}
 & LDBC SPB & & {\bf x} & &  &  \\
\cline{2-7}
 & LinkGen & & {\bf x} & &  &  \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & {\bf x} & x  &  \\
\cline{2-7}
  & gMark & & x & {\bf x} & x  &  \\
\cline{2-7}
  & graphGen & & & {\bf x} &  &  \\
\hline
\hline %  ======================   social networks
\multirow{8}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x}  & \\
\cline{2-7}
 & \cite{Yao2011}  & & & & {\bf x}  & \\
\cline{2-7}
 & LinkBench  & & & x & {\bf x}  & \\
\cline{2-7}
 & S3G2  & & x & x & {\bf x}  & \\
\cline{2-7}
 & SIB & & x & & {\bf x}  &  \\
\cline{2-7}
 & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x}  & \\
\cline{2-7}
 & LDBC SNB   & & x & x & {\bf x}  & \\
\cline{2-7}
  & \cite{Nettleton2016}  & & & & {\bf x}  &  \\
%\hline
%\hline   % ======================   graph analytics
%\multirow{1}{*}{\rot{\textbf{A}}}
%  & HPC Scal. Graph Anal.  & & & & &  \\
%\cline{2-7}
%  & Graphalytics & & & & &  \\
\hline
\hline   %  ======================  community detection
\multirow{4}{*}{\rot{\textbf{Co}}}
  & \cite{danon2005comparing} & x & & & &  {\bf x} \\
\cline{2-7}
  & LFR & x & & & &  {\bf x}  \\
\cline{2-7}
  & LFR-Overlapping & x & & & &  {\bf x} \\
\cline{2-7}
  & Stochastic Block Models & x & & & &  {\bf x} \\
%\cline{2-7}
%  & & & & &  \\
\hline
%\hline   %  ======================  streaming
%\multirow{2}{*}{\rot{\textbf{St}}}
%  & S2Gen & & & & & & & {\bf x}\\
%\cline{2-7}
%  & RSPLab & & & & & & & {\bf x} \\
%%\cline{2-7}
%%  & & & & & & \\
%\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

### 2019-08-06 generators.tex
Irena's pass (plagiarism) pp 1-10

In this section, we discuss in more detail the different graph data generators using the classification introduced before. For each category we briefly describe the key features of each of the representative examples and summarize their strengths and weaknesses. The aim is to provide the readers with a detailed look at each of the tools in the context of its competitors from the same domain.

>>>>

In this section, we discuss the various graph data generators based on the classification introduced before in more detail. For each category, we first describe the key features of each of the representative examples and summarize their strengths and weaknesses. The goal is to offer a detailed information about each of the tools in the context of its competitors from the same domain.

### 2019-08-06 generators_LinkedData.tex
Irena's pass (plagiarism) pp 1-10

\paragraph{LUBM} The use-case driven Lehigh University Benchmark (LUBM)\footnote{\url{http://swat.cse.lehigh.edu/projects/lubm/}} considers the university domain. The ontology defines 43 classes and 32 properties~\cite{Guo2005158}. In addition, the LUBM benchmark provides 14 test queries. In particular, the benchmark focuses on \emph{extensional} queries, i.e., queries which target the particular data instances of the ontology, as an opposite to \emph{intentional} queries, i.e., queries which target properties and classes of the ontology. The Univ-Bench Artificial  (UBA) data generator features repeatable and random  data generation (exploiting classical linear congruential generator, LCG, of numbers). In particular, the data which is produced by the generator are assigned zero-based indexes (i.e., the first university is named \emph{University0} and so on), thus they are reproducible at any time with the same indexes.  The generator naturally allows to specify a seed for random number generation, along with the desired number of universities, and the starting index of the universities.

An extension of LUBM, the Lehigh BibTeX Benchmark (LBBM)~\cite{Wang2005}, enables generating synthetic data for different ontologies. The data generation process is managed through two main phases: (1) the property-discovery phase, and (2) the data generation phase. LBBM provides a probabilistic model that can emulate the discovered properties of the data of a particular domain and generate synthetic data exhibiting similar properties. A Monte Carlo algorithm is employed to output synthetic data. The approach is demonstrated on the Lehigh University BibTeX ontology which consists of 28 classes along with 80 properties. The LUBM benchmark includes 12 test queries that were designed for the benchmark data. Another extension of LUBM, the University Ontology Benchmark (UOBM)\footnote{\url{https://www.cs.ox.ac.uk/isg/tools/UOBMGenerator/}}, focuses on two aspects: (1) usage of all constructs of OWL Lite and OWL DL~\cite{owl} and (2) lack of necessary links between the generated data which thus form isolated graphs~\cite{Ma:2006:TCO:2094613.2094629}. In the former case the original ontology is replaced by the two types of extended versions from which the user can choose. In the latter case cross-university and cross-department links are added to create a more complex graph.

>>>>

\paragraph{LUBM} The use-case driven Lehigh University Benchmark (LUBM)\footnote{\url{http://swat.cse.lehigh.edu/projects/lubm/}} considers the university domain. The ontology defines 43 classes and 32 properties~\cite{Guo2005158}. In addition, 14 test queries are provided in the LUBM benchmark. In particular, the benchmark focuses on \emph{extensional} queries, i.e., queries which target the particular data instances of the ontology, as an opposite to \emph{intentional} queries, i.e., queries which target properties and classes of the ontology. The Univ-Bench Artificial  (UBA) data generator features repeatable and random  data generation (exploiting classical linear congruential generator, LCG, of numbers). In particular, the data which is produced by the generator are assigned zero-based indexes (i.e., \emph{University0}, \emph{University1} etc.), thus they are reproducible at any time with the same indexes.  The generator naturally allows to specify a seed for random number generation, along with the starting index and the desired number of universities.

An extension of LUBM, the Lehigh BibTeX Benchmark (LBBM)~\cite{Wang2005}, enables generating synthetic data for different ontologies. The data generation process is managed through two main phases: (1) the property-discovery phase, and (2) the data generation phase. LBBM provides a probabilistic model that can emulate the discovered properties of the data of a particular domain and generate synthetic data exhibiting similar properties. Synthetic data are generated using a Monte Carlo algorithm. The approach is demonstrated on the Lehigh University BibTeX ontology which consists of 28 classes along with 80 properties. The LUBM benchmark includes 12 test queries that were designed for the benchmark data. Another extension of LUBM, the University Ontology Benchmark (UOBM)\footnote{\url{https://www.cs.ox.ac.uk/isg/tools/UOBMGenerator/}}, focuses on two aspects: (1) usage of all constructs of OWL Lite and OWL DL~\cite{owl} and (2) lack of necessary links between the generated data which thus form isolated graphs~\cite{Ma:2006:TCO:2094613.2094629}. In the former case the original ontology is replaced by the two types of extended versions from which the user can choose. In the latter case cross-university and cross-department links are added to create a more complex graph.

### 2019-08-06 generators_general.tex
Irena's pass (plagiarism) pp 1-10

\paragraph {R-MAT} R-MAT (\emph{R}ecursive \emph{Mat}rix) is a procedural
synthetic graph generator which is designed to generate power-law degree
distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}.  The generator is recursive
and employs a fairly small number of parameters.  In principle, the strategy of
this generator is to achieve simple means to produce graphs that are matching
the properties of the real graphs. In particular, the design goal of R-MAT is to
produce graphs which mimics the degree distributions, imitate a community
structure and have a small diameter. R-MAT can generate weighted, directed and
bipartite graphs.

@@

\paragraph{BTER} BTER (Block Two-Level
Erd\"{o}s-R\'{e}ny)~\cite{kolda2014scalable} is a graph generator based on the
creation of multiple Erd\"{o}s-R\'{e}ny graphs with different connection
probabilities  of which they are connected randomly between them. As the main feature, BTER is able
to reproduce input degree distributions and average clustering
coefficient per degree values. The generator starts by grouping the vertices
by degree $d$, and forming groups of size $d+1$ of nodes with degree $d$. Then, these
groups are assigned an internal edge probability in order to match the observed
average clustering coefficient of the nodes of such degree. Based on this
probability, for each node, the excess degree (i.e, the degree that in
expectation will not be realized internally in the group) is computed and used to connect
nodes from different groups at random. The authors describe a highly scalable
MapReduce based implementation that is capable of generating large graphs (with
billions of nodes) in a reasonable amounts of time.

@@

\paragraph{RTG} \emph{The Random Typing Generator} (RTG)~\cite{DBLP:journals/datamine/AkogluF09} aims at generating realistic graphs. In particular, it outputs (un)weighted, (un)directed, as well as uni/bipartite graphs, whereas the realism of the output is ensured by 11 laws (e.g., densification power law, weight power law, small and shrinking diameter, community structure, etc.) known to be typically exhibited by real-world graphs. On input it requires 4 parameters ($k$, $q$, $W$, and $\beta$) that correspond to the core Miller's observation~\cite{miller1957} that a random process (namely, random typing of $W$ words on a keyboard with $k$ characters and a space, where a space is hit with probability $q$ and other characters with probability $(1-q)/k$) leads to Zipf-like power laws (of the resulting words) plus in addition (using imbalance factor $\beta$) ensure homophily and community structure. RTG is based on the idea of connecting each pair of consecutive words by an edge.

@@

\paragraph{Strengths and Weaknesses of General Graph Generators}
In general, existing general graph generators produce graphs with the following
properties: skewed degree distribution (e.g., powerlay), small diameter, large
clustering coefficient, a large largest connected component, and some degree of
community structure. Degree distribution can be typically configured while other
properties are just a result of the generation process and cannot be controlled
by any means.

>>>>

\paragraph {R-MAT} R-MAT (\emph{R}ecursive \emph{Mat}rix) is a procedural
synthetic graph generator which is designed to generate power-law degree
distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}.  The generator is recursive
and employs a fairly small number of parameters.  In principle, the strategy of
this generator is to achieve simple means to produce graphs whose properties correspond to 
properties of the real-world graphs. In particular, the design goal of R-MAT is to
produce graphs which mimics the degree distributions, imitate a community
structure and have a small diameter. R-MAT can generate weighted, directed and
bipartite graphs.

@@

\paragraph{BTER} BTER (Block Two-Level
Erd\"{o}s-R\'{e}ny)~\cite{kolda2014scalable} is a graph generator based on the
creation of multiple Erd\"{o}s-R\'{e}ny graphs with different connection
probabilities  of which they are connected randomly between them. As the main feature, BTER is able
to reproduce input degree distributions and average clustering
coefficient per degree values. The generator starts by grouping the vertices
by degree $d$, and forming groups of size $d+1$ of nodes with degree $d$. Then, these
groups are assigned an internal edge probability in order to match the observed
average clustering coefficient of the nodes of such degree. Based on this
probability, for each node, the excess degree (i.e, the degree that in
expectation will not be realized internally in the group) is computed and used to connect
nodes from different groups at random. The authors describe a highly scalable
MapReduce-based implementation that is able to generate large graphs (consisting of
billions of nodes) in a reasonable amounts of time.

@@

\paragraph{RTG} \emph{The Random Typing Generator} (RTG)~\cite{DBLP:journals/datamine/AkogluF09} aims at generating realistic graphs. In particular, it outputs (un)weighted, (un)directed, as well as uni/bipartite graphs, whereas the realism of the output is ensured by 11 laws (e.g., densification power law, weight power law, small and shrinking diameter, community structure, etc.) known to be typically exhibited by real-world graphs. On input it requires 4 parameters ($k$, $q$, $W$, and $\beta$) that correspond to the core Miller's observation~\cite{miller1957} that a random process (namely, having a keyboard with $k$ characters and a space, the process of random typing of $W$ words, where the probability of hitting a space is $q$ and the probability of hitting any other characters is $(1-q)/k$) leads to Zipf-like power laws (of the resulting words) plus in addition (using imbalance factor $\beta$) ensure homophily and community structure. RTG is based on the idea creating an edge between pairs of consecutive words.

@@

\paragraph{Strengths and Weaknesses of General Graph Generators}
In general, existing general graph generators produce graphs with the following
properties: skewed degree distribution (e.g., powerlay), small diameter, a large largest connected component, large
clustering coefficient, and some degree of
community structure. Degree distribution can be typically configured while other
properties are just a result of the generation process and cannot be controlled
by any means.

### 2019-08-06 introduction.tex
Irena's pass (plagiarism) pp 1-10

In this survey, we provide a comprehensive overview of the state-of-the-art
modern
graph generators by focusing on those that are pertinent and suitable for
data-intensive tasks. Our aim is to cover a wide range of currently popular
areas of graph data processing. In particular, we consider graph generation
in the areas of Semantic Web, graph databases, social networks, and community detection, along with general graphs. Despite the disparate requirements of modern graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators. The reasons for this scope and classification are as follows:

@@

\paragraph*{Contributions} Our survey revisits the representatives of
modern graph data generators and summarizes their main characteristics. The comprehensive review and analysis make this paper useful for motivating new graph data generation mechanisms as well as serving as a main technical reference for selecting suitable solutions. In particular, the introductory categorization and comparative study enables the reader to quickly get his/her bearings in the field and identify a subset of generators of his/her interest. Since we do not limit the survey to a particular area of graph data management,  the reader can get a broader scope in the field. Hence, while practitioners can find a solution in another previously unexpected area, researchers can identify new target areas or exploit successful results in new fields. Last but not least, %to provide a global view of the state-of-the-art, we also provide an overview of most commonly used real-world testing graph datasets. And, finally,
we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.

@@

To the best of our knowledge, our work is the first to survey the broad
landscape of graph data generators spanning different data-intensive applications and
targeting many computer science subfields. In particular, we cover Semantic Web, graph databases, social networks, and community detection, along with general graphs. However, the literature is still lacking a comprehensive study of graph generators  for many of the specific subfields mentioned above.

@@

Aggarwal and Subbian~\cite{AggarwalS14} have surveyed the evolution of analysis in
graphs, by primarily focusing on data mining maintenance methods and on analytical
quantification and explanation of the changes of the underlying networks.
A brief discussion on evolutionary
network data generators is carried out in
the paper. The data generation of evolutionary networks is based on the
Densification Power Law (DPL) and shrinking diameters, community-guided
attachment properties~\cite{Leskovec:2005:GOT:1081870.1081893}.
Generation of graphs tackling Kronecker
recursion with recursive tensor multiplication~\cite{AkogluMF08} is then considered in the above survey.
We refer the readers to the aforementioned survey for evolutionary network generators and further
discuss the open challenges of evolving graph data in Section~\ref{sec:challenges}.
%\TODO{Better highlight the differences when Sherif's part is in.}

@@

\paragraph*{Outline} The rest of this paper is organized as follows: Section~\ref{sec:comparison}
provides the opening categorization and comparison of the generators. Section~\ref{sec:generators}
provides an overview of the existing graph data generators and their main features in the frame of
the proposed categories.
%To provide a complete overview,  we list the most commonly used testing data sets for the particular categories in Section~\ref{sec:data_sets}.
In Section~\ref{sec:challenges}, we highlight some of the challenges and open problems of graph
data synthesis before we conclude in Section~\ref{sec:conclusion}.

>>>>

In this survey, we provide a detailed overview of the state-of-the-art
modern
graph generators by focusing on those that are pertinent and suitable for
data-intensive tasks. Our aim is to cover a wide range of currently popular
areas of graph data processing. In particular, we consider graph generation
in the areas of Semantic Web, graph databases, social networks, and community detection, along with general graphs. Despite the disparate requirements of modern graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators. The reasons for this scope and classification are as follows:

@@

\paragraph*{Contributions} Our survey revisits the representatives of
modern graph data generators and summarizes their main characteristics. The detailed review 
and analysis make this paper useful for stimulating new graph data generation mechanisms as well as 
serving as a main technical reference for selecting suitable solutions. In particular, the introductory 
categorization and comparative study enables the reader to quickly get his/her bearings in the field and 
identify a subset of generators of his/her interest. Since we do not limit the survey to a particular area of graph data management,  the reader can get a broader scope in the field. Hence, while practitioners can find a solution in another previously unexpected area, researchers can identify new target areas or exploit successful results in new fields. Last but not least, %to provide a global view of the state-of-the-art, we also provide an overview of most commonly used real-world testing graph datasets. And, finally,
we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.

@@

To the best of our knowledge, this paper is the first to survey the broad
landscape of graph data generators spanning different data-intensive applications and
targeting many computer science subfields. In particular, we cover Semantic Web, graph databases, social networks, and community detection, along with general graphs. However, the literature is still lacking a comprehensive study of graph generators  for many of the specific subfields mentioned above.

@@

Aggarwal and Subbian~\cite{AggarwalS14} have surveyed the evolution of analysis in
graphs, by primarily focusing on data mining maintenance methods and on analytical
quantification and explanation of the changes of the underlying networks.
A brief discussion on evolutionary
network data generators is carried out in
the paper. The data generation of evolutionary networks is based on the
shrinking diameters and Densification Power Law (DPL), i.e., community-guided
attachment properties~\cite{Leskovec:2005:GOT:1081870.1081893}.
Generation of graphs tackling Kronecker
recursion with recursive tensor multiplication~\cite{AkogluMF08} is then considered in the above survey.
We refer the readers to the aforementioned survey for evolutionary network generators and further
discuss the open challenges of evolving graph data in Section~\ref{sec:challenges}.
%\TODO{Better highlight the differences when Sherif's part is in.}

@@

\paragraph*{Outline} The rest of the text is structured as follows: Section~\ref{sec:comparison}
provides the opening categorization and comparison of the generators. Section~\ref{sec:generators}
provides an overview of the existing graph data generators and their main features in the frame of
the proposed categories.
%To provide a complete overview,  we list the most commonly used testing data sets for the particular categories in Section~\ref{sec:data_sets}.
In Section~\ref{sec:challenges}, we highlight some of the challenges and open problems of graph
data synthesis before we conclude in Section~\ref{sec:conclusion}.
